Demographic survey on Toronto shelter

### 2024-09-24 paper/paper.qmd
update paper writing

# Load the dataset (update with your file path)
data <- read.csv("/Users/XiziS/OneDrive/Desktop/1/Toronto_shelter_research/starter_folder-main (1)/data1.csv")

@@

# Load the dataset (update the file path)
data <- read.csv("/Users/XiziS/OneDrive/Desktop/1/Toronto_shelter_research/starter_folder-main (1)/data1.csv")

>>>>

# Load the dataset (update with your file path)
data <- read.csv("/Users/XiziS/OneDrive/Desktop/1/Toronto_shelter_research/data/analysis_data/trtdata1.csv")

@@

# Load the dataset (update the file path)
data <- read.csv("/Users/XiziS/OneDrive/Desktop/1/Toronto_shelter_research/data/analysis_data/trtdata1.csv")
